Illusory Finger Stretching and Somatosensory Responses

### 2025-06-17 manuscript.qmd
Added download code for new figures

>>>>

if (!file.exists('Figures/exploratoryeegdata.png')){
  osfproject <- osf_retrieve_node("wfu7j")
  osffiles <- osf_ls_files(osfproject,n_max=100)
  fid <- which(osffiles$name=='exploratoryeegdata.png')
  osf_download(osffiles[fid,], path='Figures/',progress=TRUE)
}

if (!file.exists('Figures/correlationdata.pdf')){
  osfproject <- osf_retrieve_node("wfu7j")
  osffiles <- osf_ls_files(osfproject,n_max=100)
  fid <- which(osffiles$name=='correlationdata.pdf')
  osf_download(osffiles[fid,], path='Figures/',progress=TRUE)
}
